Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic data sets with *mice*

### 2021-10-05 manuscript/Manuscript.tex
final draft

% Authors, for the paper (add full first names)
\Author{Thom
Volker$^{1,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

@@

% Simple summary
\simplesumm{A Simple summary goes here.}

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

@@

\begin{longtable}[]{@{}ll@{}}
\toprule
column & description \\
\midrule
\endhead
age & age in years \\
hgt & height (cm) \\
wgt & weight (kg) \\
bmi & body mass index \\
hc & head circumference (cm) \\
gen & genital Tanner stage G1-G5 \\
phb & pubic hair Tanner P1-P6 \\
tv & testicular volume (ml) \\
reg & region \\
\bottomrule
\end{longtable}

Unfortunately, this data set does not differ from the vast majority of
collected data sets, in the sense that it suffers from missing data. For
simplicity, the data is completed using the default \texttt{mice}
imputation model for all predictors except \texttt{bmi}, which is
passively imputed using its deterministic relation with weight and
height.

@@

To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
data will be synthesized with \(m = 5\) imputations. Synthetic values
are generated using the \texttt{CART} imputation method for all columns,
except for \texttt{bmi}. The deterministic relation \texttt{bmi} which
will be synthesized passively based on the synthetic values for
\texttt{hgt} and \texttt{wgt} to preserve the relation in the synthetic
data. Additional parameters that come with the use of
\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
the minimum number of observations in any terminal node
\texttt{minbucket}, that both constrain the flexibility of the
imputation model. The values of the parameters \texttt{cp} and
\texttt{minbucket} ought to adhere to the call for imputation models
that are as flexible as possible. Appropriate values for these
parameters, as well as the input for the \texttt{predictorMatrix},
depend on the data at hand. In the current example, the complexity
parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
value \texttt{1e-04}, and the minimum number of observations in each
terminal node is set at \texttt{minbucket} \(= 3\) rather than the
default value \(5\). By allowing for more complexity in the imputation
model, bias in the estimates from the synthetic data set is reduced.
Additionally, since the missingness pattern is monotone, the number of
iterations can be set to \texttt{maxit\ =\ 1}.

@@

Obtaining a final point estimate of the parameter of interest \(Q\)
after imputation is fairly easy and no different from pooling in the
case of missing data \citep{rubin_multiple_1987}. One can calculate the
average of the \(m\) point estimates \(q^{(l)}\) \[
\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
\] with \(l = 1, \dots, m\).

@@

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

Subsection text here.

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:

\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}

The text continues here.

@@

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

\hypertarget{patents}{%
\section{Patents}\label{patents}}

This section is not mandatory, but may be added if there are patents
resulting from the work reported in this manuscript.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{`The authors declare no conflict of interest.'}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

>>>>

% Authors, for the paper (add full first names)
\Author{Thom
Volker$^{1,*}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

@@

% Simple summary

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Synthetic data sets can greatly improve the dissemination of
data and further analysis of private data. Generating and analyzing
synthetic data sets is straightforward, yet adopting a synthetic data
analysis pipeline is often ignored by applied researchers. We outline a
simple procedure for generating and alayzing synthetic data sets with
\texttt{mice} in \texttt{R}. We demonstrate in simulation that the
analysis results obtained on synthetic data obtained with \texttt{mice}
yields unbiased and valid inferences, and leads to synthetic records
that cannot be distinguished from the true data records. The ease of use
when synthesizing data with \texttt{mice}, together with the validity of
inferences obtained through this procedure opens up a wealth of
possibilities for data dissemination and further research of initially
private data.}

% Keywords
\keyword{mice; imputation; synthetic data.}

@@

\begin{table}[H]
\caption{Description of the features in the \texttt{mice::boys} data set.}
\centering
\begin{tabular}{rl}
\hline
column & description                \\ 
\hline
age    & age in years               \\ 
hgt    & height (cm)                \\ 
wgt    & weight (kg)                \\ 
bmi    & body mass index            \\ 
hc     & head circumference (cm)    \\ 
gen    & genital Tanner stage G1-G5 \\ 
phb    & pubic hair Tanner P1-P6    \\ 
tv     & testicular volume (ml)     \\ 
reg    & region                     \\ 
\hline
\end{tabular}
\end{table}

Unfortunately, this data set does not differ from the vast majority of
collected data sets, in the sense that it suffers from missing data. For
simplicity, we complete the missing values using the default
\texttt{mice} imputation model for all predictors except \texttt{bmi},
which is passively imputed using its deterministic relation with
\texttt{wgt} and \texttt{hgt}.

@@

To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
data have been synthesized with \(m = 5\) imputations for every data
cell. Synthetic values are generated using the \texttt{CART} imputation
method for all columns, except for \texttt{bmi}. The deterministic
relation \texttt{bmi} which will be synthesized passively based on the
synthetic values for \texttt{hgt} and \texttt{wgt} to preserve the
relation in the synthetic data. Additional parameters that come with the
use of \texttt{mice.impute.cart()} are the complexity parameter
\texttt{cp} and the minimum number of observations in any terminal node
\texttt{minbucket}, that both constrain the flexibility of the
imputation model. The values of the parameters \texttt{cp} and
\texttt{minbucket} ought to adhere to the call for imputation models
that are as flexible as possible. Appropriate values for these
parameters, as well as the input for the \texttt{predictorMatrix},
depend on the data at hand. In the current example, the complexity
parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
value \texttt{1e-04}, and the minimum number of observations in each
terminal node is set at \texttt{minbucket} \(= 3\) rather than the
default value \(5\). By allowing for more complexity in the imputation
model, bias in the estimates from the synthetic data set is reduced.
Additionally, since the synthesis pattern is monotone, the number of
iterations can be set to \texttt{maxit\ =\ 1}.

@@

Obtaining a final point estimate of the parameter of interest \(Q\)
after imputation is fairly easy and no different from pooling in the
case of missing data \citep{rubin_multiple_1987}. One can calculate the
average of the \(m\) point estimates \(q^{(l)}\) \[
\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m},
\] with \(l = 1, \dots, m\).

@@

We evaluate the synthetic data with respect to the \emph{true} data set
on the basis of three aims. We believe that every reliable and valid
data synthetisation effort in statistical data analysis should be able
to yield 1) unbiased univariate statistical properties, 2) unbiased
bivariate properties, 3) unbiased and valid multivariate inferences and
4) synthetic data that cannot be distinguished from real data. We
consider the evaluation of the synthetic data simulations in the above
order.

\hypertarget{univariate-estimates}{%
\subsection{Univariate estimates}\label{univariate-estimates}}

The univariate descriptives for the original data and the synthetic data
can be found in Table 2.

\begin{table}[ht]
\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations.}
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & n & mean & sd & median & min & max & skew & kurtosis \\ 
  \hline
original age & 748 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
  synthetic age & 748 & 9.15 & 6.89 & 10.49 & 0.04 & 20.96 & -0.03 & -1.55 \\ 
  original hgt & 748 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
  synthetic hgt & 748 & 131.06 & 46.50 & 145.32 & 50.69 & 197.16 & -0.30 & -1.47 \\ 
  original wgt & 748 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
  synthetic wgt & 748 & 37.09 & 26.00 & 34.44 & 3.35 & 112.26 & 0.38 & -1.03 \\ 
  original bmi & 748 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
  synthetic bmi & 748 & 18.05 & 3.08 & 17.48 & 11.49 & 32.37 & 1.11 & 1.85 \\ 
  original hc & 748 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
  synthetic hc & 748 & 51.61 & 5.86 & 53.18 & 34.38 & 62.85 & -0.91 & 0.12 \\ 
  original gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
  synthetic gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.35 \\ 
  original phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
  synthetic phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.24 \\ 
  original tv & 748 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
  synthetic tv & 748 & 8.42 & 8.11 & 3.19 & 1.00 & 25.00 & 0.85 & -0.77 \\ 
  original reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
  synthetic reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.76 \\ 
   \hline
\end{tabular}
\end{table}

We see from Table 1 that the synthetic data estimates closely resemble
the true data estimates.

\hypertarget{bivariate-estimates}{%
\subsection{Bivariate estimates}\label{bivariate-estimates}}

An often used bivariate statistic is Pearson's correlation coefficient.
When evaluating this correlation coefficient on the numeric columns in
the \texttt{boys} data set, we find that biases are very small. The
results are displayed in Table 3.

\begin{table}[H]
\caption{Bivariate correlations of the numerical columns in the true data with in parentheses the corresponding bias of the $m=5$ pooled synthetic correlations over 1000 simulations. All estimates are rounded to 3 decimal places. }
\centering
\begin{tabular}{rcccccc}
  \hline
 & age & hgt & wgt & bmi & hc & tv \\ 
  \hline
age & 1 & 0.976 (0.001) & 0.950 (0.000) & 0.627 (0.009) & 0.853 (0.000) & 0.810 (0.002) \\ 
  hgt & 0.976 (0.001) & 1 & 0.944 (0.001) & 0.596 (0.013) & 0.907 (0.000) & 0.754 (0.000) \\ 
  wgt & 0.950 (0.000) & 0.944 (0.001) & 1 & 0.791 (0.009) & 0.834 (0.000) & 0.817 (0.000) \\ 
  bmi & 0.627 (0.009) & 0.596 (0.013) & 0.791 (0.009) & 1 & 0.588 (0.009) & 0.610 (0.007) \\ 
  hc & 0.853 (0.000) & 0.907 (0.000) & 0.834 (0.000) & 0.588 (0.009) & 1 & 0.623 (0.000) \\ 
  tv & 0.810 (0.002) & 0.754 (0.000) & 0.817 (0.000) & 0.610 (0.007) & 0.623 (0.000) & 1 \\ 
   \hline
\end{tabular}
\end{table}

We see that the correlations obtained from synthetic data are unbiased
with respect to the true data set.

\hypertarget{multivariate-model-inferences}{%
\subsection{Multivariate model
inferences}\label{multivariate-model-inferences}}

First, we evaluate the performance of our synthetic simulation set on a
linear model where \texttt{hgt} is modeled by a continuous predictor
\texttt{age} and an ordered categorical predictor \texttt{phb}. The
results for this simulation can be found in Table 4.

\begin{table}[ht]
\caption{Simulation results for a linear regression model with continuous and ordered categorical predictors. The model evaluated is `hgt ~ age + phb`. Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
\centering
\begin{tabular}{rrrrrr}
  \hline
  & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
 term & estimate & bias & cov & bias & cov \\ 
  \hline
(Intercept) & 63.087 & -0.001 & 0.970 & 0.405 & 0.958 \\ 
  age & 7.174 & 0.000 & 0.958 & -0.033 & 0.947 \\ 
  phb.L & -12.250 & 0.008 & 0.950 & 0.582 & 0.927 \\ 
  phb.Q & -1.376 & -0.022 & 0.926 & 0.112 & 0.934 \\ 
  phb.C & -3.564 & 0.051 & 0.915 & 0.301 & 0.912 \\ 
  phb\verb|^|4 & -0.431 & 0.016 & 0.930 & 0.106 & 0.940 \\ 
  phb\verb|^|5 & 2.064 & 0.060 & 0.941 & 0.077 & 0.943 \\ 
   \hline
\end{tabular}
\end{table}

We see that the finite nature of the true data set together with the
design-based simulation setup yields slight undercoverage for the
polynomial functions. This finding is observed in both the bootstrap
coverages (i.e.~the fraction of 95\% confidence intervals that cover the
true data parameters) and the synthetic data coverages, indicating that
the undercoverage stems from the simulation setup.

Second, we evaluate a proportional odds logistic regression model
wherein ordered categorical column \texttt{gen} is modeled by continuous
predictors \texttt{age} and \texttt{hc}, and categorical predictor
\texttt{reg}. The results for this model evaluation are shown in Table
5.

\begin{table}[H]
\caption{Simulation results for a proportional odds logistic regression model with continuous and ordered categorical predictors. The model evaluated is `gen ~ age + hc + reg`. Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
\centering
\begin{tabular}{rrrrrr}
  \hline
 & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
 term & estimate & bias & cov & bias & cov \\ 
  \hline
  age & 0.461 & 0.004 & 0.942 & 0.002 & 0.939 \\
  hc & -0.188 & -0.000 & 0.929 & -0.004 & 0.945 \\
  regeast & -0.339 & 0.012 & 0.960 & 0.092 & 0.957\\
  regwest & 0.486 & 0.009 & 0.952 & -0.122 & 0.944\\
  regsouth & 0.646 & 0.012 & 0.966 & -0.152 & 0.943 \\
  regcity & -0.069 & 0.012 & 0.940 & 0.001 & 0.972 \\
  G1$|$G2 & -6.322 & 0.032 & 0.934 & -0.254 & 0.946 \\
  G2$|$G3 & -4.501 & 0.052 & 0.936 & -0.246 & 0.945 \\
  G3$|$G4 & -3.842 & 0.058 & 0.937 & -0.244 & 0.948 \\
  G4$|$G5 & -2.639 & 0.064 & 0.936 & -0.253 & 0.947 \\
   \hline
\end{tabular}
\end{table}

These results demonstrate that the synthetic data analysis yields valid
inferences with low bias.

\hypertarget{data-discrimination}{%
\subsection{Data discrimination}\label{data-discrimination}}

When we combine the original and synthetic data, can we predict which
rows come from the synthetic data set? If so, then our synthetic data
procedure would be redundant, since the synthetic set differs from the
observed set. To evaluate whether we can distinguish between the true
data and the synthetic data, we combine the rows from each simulation
synthetic data set with the rows from the true data. We then run a
logistic regression model to predict group membership: i.e.~does a row
belong to the true data or synthetic data. As predictors we take all
columns in the data. The pooled parameter estimates over all simulations
can be found in Table 6.

\begin{table}[H]
\caption{Simulation results for a logistic regression model aimed at discriminating between synthetic records and true records.}
\centering
\begin{tabular}{rrrrrr}
  \hline
 term & estimate & std.error & statistic & df & p.value \\
  \hline
  (Intercept) & 0.22 & 1.15 & 0.19 & 521.93 & 0.60 \\ 
  wgt & 0.00 & 0.02 & 0.25 & 420.19 & 0.60 \\
  hgt & -0.00 & 0.01 & -0.18 & 359.73 & 0.60 \\
  age & -0.00 & 0.05 & -0.00 & 345.73 & 0.62 \\ 
  hc & 0.00 & 0.03 & 0.11 & 415.44 & 0.61\\
  gen.L & -0.00 & 0.42 & -0.00 & 164.76 & 0.65 \\
  gen.Q & -0.01 & 0.21 & -0.04 & 203.38 & 0.63 \\
  gen.C & -0.00 & 0.16 & -0.02 & 239.63 & 0.64 \\
  gen\verb|^|4 & 0.01 & 0.21 & 0.01 & 237.41 & 0.63 \\
  phb.L & -0.02 & 0.44 & -0.04 & 156.54 & 0.64 \\
  phb.Q & -0.01 & 0.22 & -0.02 & 198.20 & 0.64 \\
  phb.C & 0.00 & 0.18 & 0.00 & 211.17 & 0.62 \\
  phb\verb|^|4 & 0.00 & 0.18 & 0.02 & 228.51 & 0.64\\
  phb\verb|^|5 & 0.00 & 0.20 & 0.02 & 248.57 & 0.63\\
  tv & 0.00 & 0.02 & 0.01 & 264.26 & 0.63\\
  regeast & -0.00 & 0.23 & 0.01 & 210.90 & 0.64 \\ 
  regwest & -0.00 & 0.22 & -0.00 & 221.14 & 0.63 \\ 
  regsouth & -0.01 & 0.22 & -0.02 & 226.10 & 0.64 \\ 
  regcity & 0.01 & 0.27 & 0.03 & 204.15 & 0.64 \\ 
  bmi & -0.02 & 0.06 & -0.26 & 320.18 & 0.61 \\
   \hline
\end{tabular}
\end{table}

From these pooled results we can see that the effects for all predictors
are close to zero and non-significant. When we take the predicted values
from the simulated models and compare them with the \emph{real} values,
we obtain the summary statistics in Table 7.

\begin{table}[H]
\caption{Confusion statistics for a prediction model aimed at discriminating between synthetic records and true records.}
\centering
\begin{tabular}{rr}
  \hline
& estimate\\
  \hline
 Accuracy & 0.50381 \\
 Balanced Accuracy & 0.50381 \\
 Kappa & 0.00762 \\
 McnemarPValue & 0.63187 \\
 Sensitivity & 0.50368 \\
 Specificity & 0.50394 \\
 Prevalence & 0.50000 \\
   \hline
\end{tabular}
\end{table}

The accuracy of the predictive modeling effort is not better than random
selection and the Kappa coefficient indicates that a perfect prediction
model is far from realized. The accuracy is quite balanced as there is
no skewness over sensitivity and specificity. These findings indicate
that the synthetic data is indistinguishable from the true data.

@@

We demonstrate that generating synthetic data sets with \texttt{mice} in
\texttt{R} is a straightforward process that fits well in a data
analysis pipeline. The multiple synthetic sets yield valid inferences
about the true underlying data generating mechanism, thereby capturing
the nature of the original data. This makes the multiple synthetisation
procedure with \texttt{mice} suitable for further dissemination of
synthetic data sets.

To non-statisticians, the procedure of generating multiple synthetic
sets may seem overly complicated. We would like to emphasize that
analyzing a single synthesized set, while perhaps unbiased, would
underestimate the variance properties that are so important in drawing
statistical inferences from finite data sets. After all, we are often
not interested in the sample at hand, but in the underlying data
generating mechanism, such as the population. Properly capturing the
uncertainty of synthetic data sets, just like with incomplete data sets,
is therefore paramount.

Analyzing multiple synthetic sets has another clear benefit over
analyzing just a single synthesized data set: the risk for data
disclosure is much lower. Instead of having just one synthetic
realization, a set of multiple synthetic values that could have been are
generated from the posterior predictive distribution. This means that
both properties that might belong to individual participants, as well as
properties that might not belong to those participants can be introduced
in the synthetic values. Because we are not interested in the individual
data sets, but rather in the inference obtained over the multiple data
sets, the likelihood of data properties distributed over participants is
aggregated to represent the true data generating model.

That said, while the fields of data disclosure control and data
synthetisation originated decades ago, it is more relevant today than
ever. In our study we outline a standard research workflow where the
goal is to synthesize a complete data set. To simplify the simulation we
adopted a bootstrapping scheme to induce sampling variance in order to
conform to the combination procedure defined by
\citet{reiter_partially_inference_2003}. Ideally, one would like to omit
the bootstrap from the synthetization to adopt a scheme where the
sampled data itself serves as a reference: much like the procedure
outlined in \citet{vink2014pooling} for incomplete data simulation. The
corresponding pooling rules have not been derived yet and the
incorporation in data analysis workflows would require proper attention
from developers alike.

It is important to note that in our simulations we used a single
iteration. A single iteration is sufficient only when the true data is
completely observed {[}IBRAHIM ref needed{]}. If both observed and
unobserved values are to be synthesized, then more iterations and a
careful investigation into the convergence of the algorithm are in
order. Synthetic data generation with \texttt{mice} is therein no
different than multiple imputation with \texttt{mice}.

There are other developments that can generate synthetic data sets. For
example, the \texttt{synthpop} \citet{synthpop} package in \texttt{R}
would yield valid synthetic data sets, but requires the true data to be
completely observed. To avoid this, one could adopt a two-step approach
wherein the incomplete values are multiply imputed before
synthetization. Given \(m\) multiple imputations and synthetizations, at
least \(m^2\) synthetic data sets are then in order. The flexibility
with \texttt{mice} is that both unobserved and observed data values can
be synthesized at once, without the need for a two-step approach. With
\texttt{mice} \(m\) synthetic sets are sufficient.

The ease of use when synthesizing data with \texttt{mice} in \texttt{R},
together with the validity of inferences obtained through this procedure
opens up a wealth of possibilities for data dissemination and further
research of initially private data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{We are grateful to Mirthe Hendriks and Stijn van den
Broek for replicating the simulation study on an independent data set.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{The authors contributed equally to this work.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{A full simulation archive is available from
\url{https://github.com/amices/Federated_imputation/tree/master/manuscript}.}

### 2021-10-05 mice_synthesizing/paper.Rmd
update manuscript
final draft

synthetic_samples <- 
  bootstrap_samples %>%
  future_map(function(x) {
    x %>% mice(m = 5, 
               maxit = 1,
               method = "cart",
               minbucket = 3,
               cp = 1e-08,
               predictorMatrix = pred,
               post = post,
               where = matrix(TRUE, nrow(data), ncol(data)),
               print = F)
}, .options = furrr_options(seed = as.integer(123)))

true_age <- 
  bootstrap_samples %>%
  map_dfr(~lm(age ~ wgt + hgt, .x) %>%
            broom::tidy(conf.int = TRUE))

@@

@@

>>>>

synthetic_samples <- 
  bootstrap_samples %>%
  future_map(function(x) {
    x %>% mice(m = 5, 
               maxit = 1,
               method = "cart",
               minbucket = 3,
               cp = 1e-08,
               predictorMatrix = pred,
               post = post,
               where = matrix(TRUE, nrow(data), ncol(data)),
               print = F)
}, .options = furrr_options(seed = as.integer(123)))
```

```{r cache = TRUE}
true_age <- 
  bootstrap_samples %>%
  map_dfr(~lm(age ~ wgt + hgt, .x) %>%
            broom::tidy(conf.int = TRUE))

@@

Iets over meerdere data sets en disclosure risk. een cel can in theorie eigenschappen krijgen toegewezen die niet wenselijk zijn. dat is één van de mogelijkheden van what could have been.

@@

itereren. als missingness en synth, dan moet je itereren.
